A pipeline to analyse time-course gene expression data

### 2019-09-27 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

\begin{tabular}{llrrrlr}
\toprule
GO ID & Description & Annotated & Significant & Expected & P-value & Adj. p-value\\
\midrule
GO:0003002 & regionalization & 172 & 153 & 134.41 & 0.00026 & 0.263\\
GO:0048562 & embryonic organ morphogenesis & 152 & 135 & 118.78 & 0.00045 & 0.332\\
GO:0010970 & transport along microtubule & 82 & 75 & 64.08 & 0.00046 & 0.332\\
GO:0006805 & xenobiotic metabolic process & 49 & 47 & 38.29 & 0.00059 & 0.373\\
GO:0060173 & limb development & 92 & 84 & 71.89 & 0.00068 & 0.382\\
\addlinespace
GO:0019395 & fatty acid oxidation & 53 & 51 & 41.42 & 0.00134 & 0.619\\
GO:0055114 & oxidation-reduction process & 536 & 461 & 418.84 & 0.00139 & 0.619\\
GO:0060070 & canonical Wnt signaling pathway & 149 & 131 & 116.43 & 0.00147 & 0.619\\
GO:0090596 & sensory organ morphogenesis & 134 & 118 & 104.71 & 0.00219 & 0.852\\
GO:0060411 & cardiac septum morphogenesis & 33 & 32 & 25.79 & 0.00295 & 1.000\\
\addlinespace
GO:0010811 & positive regulation of cell-substrate ad... & 81 & 73 & 63.30 & 0.00384 & 1.000\\
GO:0042738 & exogenous drug catabolic process & 22 & 22 & 17.19 & 0.00437 & 1.000\\
GO:1901381 & positive regulation of potassium ion tra... & 22 & 22 & 17.19 & 0.00437 & 1.000\\
GO:0007368 & determination of left/right symmetry & 66 & 60 & 51.57 & 0.00536 & 1.000\\
GO:0060078 & regulation of postsynaptic membrane pote... & 66 & 60 & 51.57 & 0.00536 & 1.000\\
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llrrrlr}
\toprule
GO ID & Description & Annotated & Significant & Expected & P-value & Adj. p-value\\
\midrule
GO:0007224 & smoothened signaling pathway & 74 & 69 & 57.82 & 0.00041 & 0.326\\
GO:0010970 & transport along microtubule & 82 & 75 & 64.07 & 0.00045 & 0.326\\
GO:0048562 & embryonic organ morphogenesis & 155 & 137 & 121.10 & 0.00067 & 0.378\\
GO:0060173 & limb development & 92 & 84 & 71.88 & 0.00067 & 0.378\\
GO:0006805 & xenobiotic metabolic process & 47 & 45 & 36.72 & 0.00089 & 0.451\\
\addlinespace
GO:0060070 & canonical Wnt signaling pathway & 152 & 134 & 118.76 & 0.00099 & 0.456\\
GO:0019395 & fatty acid oxidation & 53 & 51 & 41.41 & 0.00133 & 0.562\\
GO:0055114 & oxidation-reduction process & 533 & 458 & 416.42 & 0.00152 & 0.593\\
GO:0090596 & sensory organ morphogenesis & 134 & 118 & 104.69 & 0.00216 & 0.783\\
GO:0010811 & positive regulation of cell-substrate ad... & 77 & 70 & 60.16 & 0.00260 & 0.879\\
\addlinespace
GO:0060411 & cardiac septum morphogenesis & 33 & 32 & 25.78 & 0.00293 & 0.929\\
GO:0021510 & spinal cord development & 48 & 45 & 37.50 & 0.00339 & 1.000\\
GO:0016571 & histone methylation & 74 & 67 & 57.82 & 0.00418 & 1.000\\
GO:0042738 & exogenous drug catabolic process & 22 & 22 & 17.19 & 0.00435 & 1.000\\
GO:1901381 & positive regulation of potassium ion tra... & 22 & 22 & 17.19 & 0.00435 & 1.000\\
\bottomrule
\end{tabular}
